DOpElib:\\ Differential Equations and Optimization Environment

### 2017-05-28 Examples/Documentation/introduction.tex
Docu modifications related to the new Example 8

Furthermore, there are more highly appreciated contributions
made by %(in alphabetical order)
\begin{itemize}
  \item Daniel Jodlbauer (current work on parallelization)
  \item Bernhard Endtmayer (currently working on phase-field fracture)
  \item Michael Geiger (Examples for Plasticity, and Documentation of several PDE-Examples)
  \item Masoud Ghaderi (Augmenting the Documentation)
  \item Uwe K{\"o}cher (Makefile compatibility)
  \item Francesco Ludovici (Augmenting the Documentation)
  \item Matthias Maier (CMake)
\end{itemize}

@@

The reason for this problem might be that the variables c++ and g++ as well as cc and gcc do not match.
\newline
You can remove the old Examples folder and replace it by a new one and set the compilers manually by
\begin{lstlisting}
export CXX=path/to/g++-compiler
export CC=path/to/gcc-compiler
\end{lstlisting}
where path/to/compiler should be the path to compiler DOpElib was compiled with.
You can check the current version of your gcc- and g++-compiler with 
\begin{lstlisting}
gcc --version
g++ --version
\end{lstlisting}
Alternatively you can set the variable c++ to your g++ and the variable cc to gcc using update-alternatives
as for example
\begin{lstlisting}
sudo update-alternatives --install /usr/bin/c++ c++ /usr/bin/g++-6 60
sudo update-alternatives --install /usr/bin/cc cc /usr/bin/gcc-6 60
\end{lstlisting}
Thanks to Florian Tischler (Admin at RICAM Linz) for the help.

>>>>

Furthermore, there are more highly appreciated contributions
made by %(in alphabetical order)
\begin{itemize}
  \item Daniel Jodlbauer (current work on parallelization)
  \item Bernhard Endtmayer (phase-field fracture, PDE Instat Example 8 - in cooperation with T. Wick)
  \item Michael Geiger (Examples for Plasticity, and Documentation of several PDE-Examples)
  \item Masoud Ghaderi (Augmenting the Documentation)
  \item Uwe K{\"o}cher (Makefile compatibility)
  \item Francesco Ludovici (Augmenting the Documentation)
  \item Matthias Maier (CMake)
\end{itemize}

@@

The reason for this problem might be that the variables c++ and g++ as well as cc and gcc do not match.
\newline
You can remove the old Examples folder and replace it by a new one and set the compilers manually by
\begin{lstlisting}
export CXX=path/to/g++-compiler
export CC=path/to/gcc-compiler
\end{lstlisting}
where path/to/compiler should be the path to the compiler, DOpElib was compiled with.
You can check the current version of your gcc- and g++-compiler with 
\begin{lstlisting}
gcc --version
g++ --version
\end{lstlisting}
Alternatively you can set the variable c++ to your g++ and the variable cc to gcc using update-alternatives
as for example
\begin{lstlisting}
sudo update-alternatives --install /usr/bin/c++ c++ /usr/bin/g++-6 60
sudo update-alternatives --install /usr/bin/cc cc /usr/bin/gcc-6 60
\end{lstlisting}
Thanks to Florian Tischler (Admin at RICAM Linz) for the help.
